Setting up Data

### 2020-01-10 doc/totalSC.Rmd
working on organizing and analyzing all of the BivData. mice from MM have BivData

@@

```{r mixed.models.setup, echo=FALSE, warning=FALSE}
#https://rcompanion.org/handbook/G_03.html
#testing random effects within lme
#notes for testing random effects

@@

#mean_co.HQ  (this might remove some of the MOLF males)
DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel[DF.HetC.MixedModel$Ncells > 9,]
DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[DF.HetC.MixedModel.HQ$age.weeks < 25,]
DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[!(is.na(DF.HetC.MixedModel.HQ$mouse)|DF.HetC.MixedModel.HQ$mouse==""),]

@@

```{r check.lists, echo=FALSE}

MLH1.merge.Skel
OG.MLH1.merge.Skel

@@

@@

#curated Biv data doesn't have '.tif' -- remove .tif
skel.mice_from.MM.DF$fileName <- as.character(skel.mice_from.MM.DF$fileName)

for(j in 1:length(skel.mice_from.MM.DF$fileName)){
  print(j) 
  #MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
   templist2 = strsplit(skel.mice_from.MM.DF$fileName[j], split=".tif")#[[1]]
   #print(templist2)
   skel.mice_from.MM.DF$fileName2[j] <- templist2 #should match file name
}

DF <- skel.mice_from.MM.DF[ skel.mice_from.MM.DF$fileName2 %in% Curated_BivData$fileName, ]#299
#above is the DF which there are cell which have been curated
#merge --

DF <- add_strain(DF)
DF <- add_sex(DF)
DF <- add_category(DF)

table(DF$category) #missing MSM females

#this table now has merged bin/skel, and have been curated (but it doesn't have data on the curated bivalents)

#skel.mice_from.MM.DF$fileName %in% Curated_BivData$fileName

>>>>

#Curated list

#strain specific xlsx sheets

@@

```{r grab.nice.mice.setup, echo=FALSE, warning=FALSE}
#https://rcompanion.org/handbook/G_03.html
#testing random effects within lme
#notes for testing random effects

@@

#mean_co.HQ  (this might remove some of the MOLF males)
DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel[DF.HetC.MixedModel$Ncells > 9,]
#DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[DF.HetC.MixedModel.HQ$age.weeks < 25,]
#above should only apply to males

DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[!(is.na(DF.HetC.MixedModel.HQ$mouse)|DF.HetC.MixedModel.HQ$mouse==""),]

@@

```{r check.lists, echo=FALSE}
#MLH1.merge.Skel
#OG.MLH1.merge.Skel

@@

#some WSB females missing from DF.HETC.HQ

@@

#OG.MLH1.merge.Skel doesn't have '.tif' -- remove .tif to make matching easier
skel.mice_from.MM.DF$fileName <- as.character(skel.mice_from.MM.DF$fileName)

for(j in 1:length(skel.mice_from.MM.DF$fileName)){
  print(j) 
  #MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
   templist2 = strsplit(skel.mice_from.MM.DF$fileName[j], split='.tif')[[1]]
   #print(templist2)
   skel.mice_from.MM.DF$fileName2[j] = templist2
}
#this loop puts list in fileName2

library(tidyr)

skel.mice_from.MM.DF$og.fileName <- skel.mice_from.MM.DF$fileName
skel.mice_from.MM.DF <- skel.mice_from.MM.DF %>% separate(fileName, c("fileName3","blah"),'.tif')

#cell level data, MLH1 and skel
DF <- skel.mice_from.MM.DF[ skel.mice_from.MM.DF$fileName3 %in% Curated_BivData$fileName, ]#415
#above is the DF which there are cell which have been curated (and there is total.sc data)
#how to merge the biv level data..?

#number of bivs curated?

SC.pass_table <- ddply(.data=Curated_BivData, 
                 .(fileName),
                 summarize, 
                 n.SC.pacc.bivs = length(unique(Obj.ID))

)
#the PWD and KAZ duplicate mice will have more than 20 -- remove them

SC.pass_table <- add_mouse(SC.pass_table)
#SC.pass_table <- add_strain(SC.pass_table)
#SC.pass_table <- add_sex(SC.pass_table)
#SC.pass_table <- add_category(SC.pass_table)

DF$fileName <- DF$fileName3

#with mouse, merge to DF
DF.2 <- merge(DF, SC.pass_table, by = "fileName", all.y = FALSE, no.dups = TRUE )
#not merging because of silly / weird list thing

DF.2 <- DF.2[ -c(14,15,20,23,21) ]
DF.2$mouse <- DF.2$mouse.x

DF.2 <- add_strain(DF.2)
DF.2 <- add_sex(DF.2)
DF.2 <- add_category(DF.2)

table(DF.2$category)

this.plot <- ggplot(DF.2, aes(n.SC.pacc.bivs)) + geom_histogram(bins = 40)+ facet_wrap(~category)+ggtitle("Number of curated bivs per image")

this.plot_WSB.female <- ggplot(DF.2[DF.2$category == "WSB female",], aes(n.SC.pacc.bivs)) + geom_histogram(bins = 40)+ facet_wrap(~mouse)+ggtitle("Number of curated bivs per image")

```{r more.blahs, echo=FALSE}

#WSB -- WSB_curation, WSB_female output on big External
#not sure why Curated bivData catching more categories than this above

#this table now has merged bin/skel, and have been curated (but it doesn't have data on the curated bivalents)
#the curated list is the current bottle neck

#I should start inventory  how many mice are in each curated category

### 2020-01-10 src/SetupData.Rmd
working on organizing and analyzing all of the BivData. mice from MM have BivData

original_DF = MLH1_data
original_DF$fileName <- (original_DF$Original.Name)
original_DF <- add_mouse(original_DF)

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")

>>>>

original_DF = MLH1_data
original_DF$fileName <- (original_DF$Original.Name)

original_DF <- add_mouse(original_DF)
original_DF <- add_strain(original_DF)
original_DF <- add_category(original_DF)
original_DF <- add_sex(original_DF)

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_1.10.20.RData")
